Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-05-06 gullydiss.tex
The grad school requires BA Astro and Phys, instead of BA, for my previous degree
incorporate ALK comments on the abstract, acknowledge family and friends

\previousdegrees{B.A.}
     % The abbreviated form of your previous degree(s).
     % E.g., \previousdegrees{B.S., MBA}.
     %
     % The default value is `B.S., M.S.'

@@

I am delighted to acknowledge support from the NASA Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA APRA grant NNX10AC68G, NASA ACT grant NNX12AC31G, NSF ATI grant AST-0705064, and NASA Origins grant number NNX07AI83G.  MGS acknowledges support from the University of Texas in the form of the Graduate Dean's Prestigious Fellowship and from the Department of Astronomy in the form of the David Benfield Memorial Fellowship in Astronomy.  Funding from the McDonald Observatory and the Department of Astronomy's Cox graduate student excellence funds have helped to support travel and other aspects of this research.  Part of the research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.  Some of the work was carried out at the University of Texas under a contract from the University of Arizona.  The development work for the grisms was supported in part by NASA (grant number NNX07AV15H).  The authors wish to thank Gary Poczulp and the National Optical Astronomy Observatory for assistance in producing some interferograms of early grating prototypes.  This dissertation includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.

%I was lucky to be part of such a talented and creative group of incoming graduate students.  Thank you to all the friendly, funny, and courageous people of Austin I met along the way---too numerous to identify---for contributing to my prosperity here.  And of course thank you to my family and friends.

@@

I summarize the optical design, fabrication, and performance of silicon diffractive optics for astronomical spectrographs.  The first set of optical devices includes diffraction-limited, high-throughput silicon grisms for JWST-NIRCam.  These grisms served as pathfinders to Silicon immersion gratings, which offer size and cost savings for high-resolution near-infrared spectrographs.  I demonstrate the production and optical evaluation of the immersion grating that enabled IGRINS at the McDonald Observatory.  This grating provides spectral resolution $R=40,000$ over the $H-$ and $K-$ near-infrared band atmospheric windows (1.5$-$2.5 $\mu$m).  Electron-beam lithography offers much higher precision over contact mask photolithography for the production of Si immersion gratings.  Using electron-beam lithography, I designed, fabricated, and tested diffraction-limited Si immersion gratings over a 30 $\times$ 100 mm beam.  These prototypes are stepping stones to monolithic Si gratings for iSHELL and GMTNIRS.  The monolithic design of Si immersion gratings presents a limitation for scaling up the grating size, since existing fabrication equipment cannot handle monolithic silicon pucks.  The size limitation can be overcome by direct-bonding Si substrates to optical prisms.  I demonstrate a technique to measure interfacial gaps as small as 14 nm between the bonding interface, which produces 0.2\% transmission loss.  These technologies will enable the direct measurement of the atmospheric properties of extrasolar planets in the next decade.

The lowest mass objects in nearby star forming regions now accessible to spectroscopy are in the sub-brown dwarf regime, with estimated masses comparable to the masses of extrasolar planets and bordering the threshold of opacity limited fragmentation.  We confirm and characterize, using $R\sim 2000$ near-infrared spectroscopy, 17 candidate young substellar objects in nearby star forming regions.  Using deep optical, near-infrared, and mid-infrared photometry, I search an off-core region of the nearby $\sim1 Myr$ \emph{Ophiuchus} star forming cluster for candidate young stars and brown dwarfs.  Multi-object $I-$band spectroscopy of 419 candidates reveals 12 new young stars and brown dwarfs.  Ten of these have no evidence for mid-IR emission from 3.6 to 8.0 $\mu$m.  The other two are indicative of edge-on disks, based on their mid-infrared slopes rising with wavelength.  The disk fraction for spectral types M4 and later towards this region of \emph{Ophiuchus} is 33\%, lower than the typical disk fraction of $1-3$ Myr clusters.

>>>>

\previousdegrees{B.A. ASTRO. \& PHYS.}
     % The abbreviated form of your previous degree(s).
     % E.g., \previousdegrees{B.S., MBA}.
     %
     % The default value is `B.S., M.S.'

@@

I am delighted to acknowledge support from the NASA Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA APRA grant NNX10AC68G, NASA ACT grant NNX12AC31G, NSF ATI grant AST-0705064, and NASA Origins grant number NNX07AI83G.  MGS acknowledges support from the University of Texas in the form of the Graduate Dean's Prestigious Fellowship and from the Department of Astronomy in the form of the David Benfield Memorial Fellowship in Astronomy.  Funding from the McDonald Observatory and the Department of Astronomy's Cox graduate student excellence funds have helped to support travel and other aspects of this research.  Part of the research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.  Some of the work was carried out at the University of Texas under a contract from the University of Arizona.  The development work for the grisms was supported in part by NASA (grant number NNX07AV15H).  The authors wish to thank Gary Poczulp and the National Optical Astronomy Observatory for assistance in producing some interferograms of early grating prototypes.  Thank you to David Hogg, Dan Foreman-Mackey, Jonathan Sick, Jake Vanderplas, and the participants and organizers of the Astro Data Hack Week (2014).  This dissertation includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.

I was lucky to be part of such a talented and creative group of incoming graduate students- Chris, John, Chalence, JJ, Julie, Manuel, Erik, Paul, and Manos.  I look forward to following their promising careers, and crossing paths indefinitely.  Joi Ito and the Minor Mishap Marching Band enhanced my creativity.  Thank you to my supportive family members Diana, Tony, Erika, and Vanessa who gave me mettle.  Thank you to Carol Contillo for bringing Chelsey into the world, to Alese for introducing us, and to Chelsey for being exceptionally supportive.  Thanks to all my friends.  I acknowledge the kindness of the Wolchover family, who have always been out standing in their field.

@@

I summarize the optical design, fabrication, and performance of silicon diffractive optics for astronomical spectrographs.  The first set of optical devices includes diffraction-limited, high-throughput silicon grisms for JWST-NIRCam.  These grisms served as pathfinders to Silicon immersion gratings, which offer size and cost savings for high-resolution near-infrared spectrographs.  I demonstrate the production and optical evaluation of the immersion grating that enabled IGRINS at the McDonald Observatory.  This grating provides spectral resolution $R=40,000$ over the $H-$ and $K-$ near-infrared band atmospheric windows (1.5$-$2.5 $\mu$m).  Electron-beam lithography offers much higher precision over contact mask photolithography for the production of Si immersion gratings.  Electron-beam patterned prototypes are stepping-stones to monolithic Si gratings for iSHELL and GMTNIRS.  The monolithic design of Si immersion gratings presents a limitation for scaling up the grating size, since existing fabrication equipment cannot handle monolithic silicon pucks.  The size limitation can be overcome by direct-bonding Si substrates to optical prisms.  I demonstrate a technique to measure interfacial gaps as small as 14 nm between the bonding interfaces, which produce 0.2\% transmission loss.  These technologies will enable the direct measurement of the atmospheric properties of extrasolar planets in the next decade.  IGRINS is now measuring fundamental properties of young \emph{T-Tauri} stars; low mass young brown dwarfs are below the sensitivity limit of existing high spectral resolution near-IR spectrographs.  My approach to the discovery and characterization of young brown dwarfs therefore employs low resolution ($R\sim 2000$) near-IR spectroscopy.  I confirm and characterize 17 candidate young stars and brown dwarfs reported by Allers and collaborators.  All 17 sources have circumstellar disks.

Using deep optical, near-infrared, and mid-infrared photometry, I search an off-core region towards the nearby $\sim1 Myr$ \emph{Ophiuchus} star forming cluster for candidate young stars and brown dwarfs.  Multi-object $I-$band spectroscopy of 419 candidates reveals 12 new members.  Ten of these have no evidence for mid-IR excess emission from 3.6 to 8.0 $\mu$m.  The disk fraction for spectral types M4 and later towards this region of \emph{Ophiuchus} is 5/15.  Two of the disk sources have edge-on disks, pointing to a high edge-on disk fraction.  I discuss possible sources of contamination in the survey.
